meta-analysis

### 2017-04-28 Code/4_combined-meta-regression.Rmd

```{r load-data}
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results$COD_cont_yrs_width <- cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl
cod_decomp_results$COD_cont_yrs_SE <- (cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl)/3.92
```

#calculated the sum of the residuals for each state-sex-cod strata (summed over years)
cod_decomp_results <- cod_decomp_results %>% 
  group_by(state, sex, COD) %>%
  mutate(sum.residual = sum(abs(resid.FE)))
```

@@

```{r save_data}
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
```

>>>>

```{r load-data}
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results$COD_cont_yrs_width <- cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl
cod_decomp_results$COD_cont_yrs_SE <- (cod_decomp_results$COD_cont_yrs_ucl - cod_decomp_results$COD_cont_yrs_lcl)/3.92

age_cod_results_female <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")
age_cod_results_male <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_male.csv")
age_cod_results <- rbind(age_cod_results_female, age_cod_results_male)
rm(age_cod_results_female, age_cod_results_male)

age_cod_results$age_COD_cont_yrs_SE <- (age_cod_results$age_COD_cont_yrs_ucl - age_cod_results$age_COD_cont_yrs_lcl)/3.92
age_cod_results_infants_AOC <- subset(age_cod_results, age_minbin == 0 & COD == "All other causes")
```

@@

#calculate the sum of the residuals for each state-sex-cod strata (summed over years)
cod_decomp_results <- cod_decomp_results %>% 
  group_by(state, sex, COD) %>%
  mutate(sum.residual = sum(abs(resid.FE)))
```

```{r RE_meta_regression_agecod_infants_only, echo = F}
RE.models.infants <- age_cod_results_infants_AOC %>% 
  group_by(sex) %>%
  do(fit = lmer(age_COD_cont_yrs_mean ~ bs(year, degree = 1, df = 5) + (1|state),
              weights = 1/(age_COD_cont_yrs_SE)^2, 
              data = .))

#creates a dataframe for males and females of the fitted estimates. Includes state variable, but we need to add on the year variable
RE.pred.infants <- broom::augment(RE.models.infants, fit)
RE.pred.infants$year <- 1969:2013

RE.models.infants$RE.estimates <- purrr::map(RE.models.infants$fit, ~ ranef(.x))

sex.infants <- c(rep("Female", 40), rep("Male", 40))
COD.infants <- rep("All other causes", 80)
RE.estimates.infants <- c(RE.models.infants$RE.estimates[[1]]$state$`(Intercept)`, RE.models.infants$RE.estimates[[2]]$state$`(Intercept)`)
state.infants <- rep(levels(age_cod_results$state), 2)
REs.infants <- data.frame(sex.infants, COD.infants, RE.estimates.infants, state.infants)
REs.infants <- REs.infants %>% rename(sex = sex.infants, COD = COD.infants, RE.estimates = RE.estimates.infants, state = state.infants)

#merge in the RE estimates to the original dataset
age_cod_results_infants_AOC <- merge(age_cod_results_infants_AOC,
                            REs.infants, by = c("sex", "state"), #state-specific REs; don't need time for merge (because time fixed)
                            all.x = T)

#merge other aspects, like the FE, with original dataset
age_cod_results_infants_AOC <- merge(age_cod_results_infants_AOC, 
                             RE.pred.infants %>% select(sex, state, year, .fitted, .resid, .fixed), 
                             by = c("sex", "state", "year"))

age_cod_results_infants_AOC <- age_cod_results_infants_AOC %>% rename(fitted.RE = .fitted, fixed.from.RE = .fixed, resid.RE = .resid)
```

```{r save_data}
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")

write.csv(age_cod_results_infants_AOC, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_infants_AOC.csv")
```
